---
title: "Trabalho de Análise de Sobrevivência"
subtitle: ""
author: Edimar, Jossivana Macedo, Douglas Vinícius
institute: Universidade Federal de Rondônia
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 9pt
output:
  beamer_presentation:
    theme: "Madrid"
    colortheme: "whale"
    fonttheme: "structurebold"
    incremental: false
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE, 
                      echo = FALSE, 
                      fig.align = 'center')
library(RefManageR)
library(tidyverse)
bibs <- ReadBib("bio.bib", check = FALSE)
```

## Partes

\begin{itemize}
  \item Introdução
  \item Banco de dados
  \item 
\end{itemize}

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Referências

```{r, results='asis'}
print(bibs[key = c("")], 
      .opts = list(check.entries = FALSE, 
                   style = "latex", 
                   bib.style = "authoryear"))
```